\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-12 final/article.tex
Add pix

	Using this predicted graph R(x,y,z) we provide tangent-line and secant-line predictions such that we provide a recommended pace for a runner such that given their current performance they achieve, exceed, or relax compared to their usual performance.  This step essentially merges our predictive data with the runner's current activity and would be the useful user-facing data provided in a retail application of our algorithms.\\

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{overlap_run.png}
\caption{A graph of pace from an actual run (shown in red) and a graph of the predicted pace (shown in blue). }
\end{center}
\end{figure}

	Using this predicted graph R(x,y,z) we provide tangent-line and secant-line predictions such that we provide a recommended pace for a runner such that given their current performance they achieve, exceed, or relax compared to their usual performance.  This step essentially merges our predictive data with the runner'۪s current activity and would be the useful user-facing data provided in a retail application of our algorithms.\\

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{overlap_run.png}
\caption{A graph of pace from an actual run (shown in red) and a graph of the predicted pace (shown in blue).  }
\end{center}
\end{figure}
